\chapter{Conclusion}

In this work we proposed an enhancement to the \acrlong{wsol} task to evaluate localization of multiple object instances. We have argued that none of existing \acrshort{wsol} evaluation metrics are suited to quantitatively measure multi-instance localization performance. We have then formally defined a new evaluation methodology and metrics to measure multi-instance object localization accuracy for a CAM-family of localization methods, requiring only standard classification models.

We validated our methodology quantitatively using localization methods (CAM, Grad-CAM, Grad-CAM++, MinMaxCAM, Score-CAM) for well-known CNN models (standard VGG16 and ResNet-50, and modified VGG16-GAP) and datasets (synthetic and ImageNet), measuring precision and recall for datasets with ground truth bounding box and segmentation mask annotations.

We demonstrated that multi-instance localization recall metrics are correlated with the number of object instances in images, and that this is valid for the assessed network architectures regularization techniques. We showed that classification and localization accuracy are correlated while training a model, and established the importance of using a trained network that has converged to reliably measure localization performance.

We proposed a novel iterative localization approach using previously predicted object localization annotations as input to improve localization recall. We demonstrated that localization recall can be improved using the right strategy to combine iterative predictions, and that this comes at the cost of a lower precision.

Our research question was whether we can use CAM-methods to evaluate and improve localization of multiple instances of the same class within images for the \acrshort{wsol} task. By proposing the \acrshort{mwsol} task, evaluating it using CAM-methods on well-known networks and dataset, and measuring multiple instance precision and recall, we demonstrated the effectiveness of our methodology. We proposed an iterative localization method and demonstrated that we could improve multiple-instance localization recall at the cost of a lower precision.

Future work involves refining the iterative localization mask strategy by using a score map segmentation mask instead of bounding box masks to apply a more fine-grained object instance search. For ImageNet we propose a split iterative localization strategy to mitigate the bias towards images with a single object instance.
