\chapter{Relationships with research projects}

\section{Relationship with "Research Project 1"}
Project information:
\begin{itemize}
    \item Research project: "Fraud detection in inheritance taxes"
    \item Internship provider: Toon Calders
    \item Supervisor: Daphne Lenders
    \item Relationship between Research Project 1 and master's thesis: Not applicable.    
\end{itemize}

In this research project I answered the question whether a successful bank investigation can be predicted for inheritance tax fraud detection using data mining techniques on highly imbalanced data. I used standard machine learning classifiers such as decision tree, random forest and logistic regression to learn a model for predicting fraud and to explain feature importance. To address class imbalance in the data I have used two different techniques: random oversampling to balance class distribution in the training data, and balanced class weights to make the classifier cost-sensitive.

\section{Relationship with "Research Project 2"}
Project information:
\begin{itemize}
    \item Research project: "Intrinsic Motivation Research in Reinforcement Learning"
    \item Internship provider: Steven Latré
    \item Supervisor: Louis Bagot
    \item Relationship between Research Project 2 and master's thesis: Not applicable.
\end{itemize}

The field of Reinforcement Learning (RL) has managed to solve very complex tasks like video games or robotic tasks without human help. However, a huge weakness of RL remains when rewards are sparse or hard to get: an agent can only act randomly in hope of discovering something rewarding. Researchers strive to generate interesting agents without rewards at all, a field sometimes called unsupervised RL. These curious agents often use intrinsic motivation to do exploration. 

In this research project I studied the theory behind the existing sub-fields and methods of Intrinsic Motivation, identified hindsight experience replay as branch of further research and explored ideas to improve learning with hindsight experience. Hindsight experience replay is a novel technique which allows learning from failures in addition to learning of success. I provided experiments in a grid world setting and a robotic control setting to support my ideas. Based on those results, I proposed possible areas of scientific research.