\chapter*{Summary}

Weakly-supervised object localization (WSOL) task has gained popularity it can be used to localize objects in images using network models trained with image-level labels only. The class activation mapping (CAM) family of WSOL methods focus on different strategies to successfully cover and localize objects. However, as these methods often use different metrics to measure object localization performance, it's difficult to benchmark them. Moreover, these metrics do not quantitatively measure localization of multiple object instances in images.

In this work we propose a multiple-instance object localization evaluation protocol. This protocol enhances existing metrics to take into account localization of multiple object instances in images. Our method uses the standard classification task and requires no additional modifications to networks or localization methods.

Using our multiple-instance object localization evaluation protocol for CAM-based localization models, we observe that the localization performance of the evaluated localization methods decreases as more object instances are present in images. This way we demonstrate that our metrics quantitatively capture multiple-instances localization performance for images with multiple object instances. We use the evaluated models as baseline for further localization performance improvements.

To improve multiple-instance localization performance, we introduce an iterative localization method, where we use localization bounding boxes predicted during previous iterations, to mask input images with those bounding boxes to mask out already found object instances images, and to subsequently find additional object instances. We demonstrate that an appropriate merge strategy for combining localization information of multiple iterations can improve localization recall substantially, but often at the cost of decreased precision. 

As future work, we expect to see further improvements in the localization of object instances by refining the iterative localization mask strategy when using a score map segmentation mask instead of bounding box masks. For ImageNet we propose a split iterative localization strategy to mitigate the bias towards images with a single object instance per image.